Learning to Group and Order AMR Semantics for General Purpose Discourse Planning

### 2015-12-10 paper/paper.tex

% TODO: comments about feature weights

>>>>

Inspecting these feature weights, we see that the most important feature is the
standard deviation for the two-apart Jaccard similarity. Having such a large
positive value indicates that the scorer prefers paragraphs that do not have
uniform overlap between a sentence and the sentence which comes second after
it. Next is the mean pairwise Jaccard similarity, which gets penalized heavily.
This would indicate that the scorer prefers paragraphs that don't have much
overlap between adjacent sentences. At first, this does not seem to make much
sense at all, as one would expect to want to have some information overlap
moving from sentence to sentence through a paragraph. However, we also observe
that the standard deviation for pairwise similarity is penalized. So, the
scorer also prefers orderings which make the information overlap through the
paragraph more uniform.
